Concurrent Programming in Harmony

### 2021-08-02 book/paper.tex
Moved some text

@@

One may wonder how failures can occur in this model.  They are not explicitly modeled, but
Harmony tries every possible execution, including executions in which some processors make
no execution steps unless there are no other processors that can run.  The way this algorithm
works, this includes executions in which $\texttt{N} - \texttt{F}$ processors terminate
before the remaining $\texttt{F}$ processors start executing.  To the first set of processors,
this is indistinguishable from executions in which the last set of processors have failed.

>>>>

One may wonder how failures can occur in this model.  They are not
explicitly modeled, but Harmony tries every possible execution.
This includes executions in which the clients terminate before
$\texttt{F}$ of the servers start executing.  To the clients, this
is indistinguishable from executions in which those
servers have failed.

@@
